---
title: "Meeting"
author: "Collin Erickson"
date: "October 3, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
setwd("..//")
knitr::opts_chunk$set(cache = TRUE)
# source("../compare_adaptconcept.R")
# getwd()
# source("C://Users//cbe117//Documents//GitHub//DOE-code//compare_adaptconcept.R")
source("adaptconcept2_sFFLHD_R6.R")
# opts_chunk$set(cache=FALSE)
library(magrittr)
```

## Progress since last week

* D=1 works
* Calculated/implemented gradient distribution


## A 1-D function with plateau and areas with large gradient

```{r cars, echo=F}

logistic <- function(x, offset, scl) {1 / (1 + exp(-scl*(x-offset)))}
logistic_plateau <- function(x) {logistic(x[1], .15, 15) - logistic(x[1], .85,15)};
curve(Vectorize(logistic_plateau)(x)); #cf(logistic_plateau)

# dir()
# getwd()
# summary(cars)
```



## Focus on large gradient norm

```{r, D1run, echo=F, message=FALSE}
set.seed(2)
csa(silent=T)
temp <- capture.output(a <- adapt.concept2.sFFLHD.R6$new(D=1,L=3,func=Vectorize(logistic_plateau), obj="desirability", des_func=des_func_grad_norm2_mean, alpha_des=1e2, n0=4, take_until_maxpvar_below=1, package="GauPro_kernel", design='sFFLHD', selection_method="max_des_red_all"))
a$run(1)
```

## Batch 2

```{r bat2, echo=FALSE}
tmp <- capture.output(a$run(1))
```

## Batch 3

```{r bat3, echo=FALSE}
tmp <- capture.output(a$run(1))
```

## Batch 4

```{r bat4, echo=FALSE}
tmp <- capture.output(a$run(1))
```

## Batch 5

```{r bat5, echo=FALSE}
tmp <- capture.output(a$run(1))
```

## Batch 6

```{r bat6, echo=FALSE}
tmp <- capture.output(a$run(1))
```

## Batch 7

```{r bat7, echo=FALSE}
tmp <- capture.output(a$run(1))
```

## Why doesn't it focus more on curves?

* Maybe the nugget is large enough so that the SE can't be reduced further

```{r}
a$mod$nugget()
```


```{r}
a$mod$predict.se(a$X) %>% summary
```

```{r}
a$mod$predict.se(a$Xopts) %>% summary 
```

## Finding plateau

* Use inverse of mean of grad norm squared

* Multiply by probability of being at least 50% of the way from min to max



## Focus on plateau

```{r, D1run2, echo=F, message=FALSE}
set.seed(2)
csa(silent=T)
temp <- capture.output(a2 <- adapt.concept2.sFFLHD.R6$new(D=1,L=3,func=Vectorize(logistic_plateau), obj="desirability", des_func=des_func_grad_norm2_meaninv_plateau, alpha_des=1e2, n0=4, take_until_maxpvar_below=1, package="GauPro_kernel", design='sFFLHD', selection_method="max_des_red_all"))
a2$run(1)
```

## Batch 2

```{r bat22, echo=FALSE}
tmp <- capture.output(a2$run(1))
```

## Batch 3

```{r bat23, echo=FALSE}
tmp <- capture.output(a2$run(1))
```

## Batch 4

```{r bat24, echo=FALSE}
tmp <- capture.output(a2$run(1))
```

## Batch 5

```{r bat25, echo=FALSE}
tmp <- capture.output(a2$run(1))
```

## Batch 6

```{r bat26, echo=FALSE}
tmp <- capture.output(a2$run(1))
```

## Batch 7

```{r bat27, echo=FALSE}
tmp <- capture.output(a2$run(1))
```


## 2D plateau

```{r, bananaplateau, echo=F, message=FALSE}
set.seed(5)
csa(silent=T)
# temp <- capture.output(a3 <- adapt.concept2.sFFLHD.R6$new(D=2,L=3,func=function(x){banana(x)^.2}, obj="desirability", des_func=des_func_grad_norm2_meaninv_plateau, alpha_des=1e2, n0=10, take_until_maxpvar_below=1, package="GauPro_kernel", design='sFFLHD', selection_method="max_des_red_all"))
temp <- capture.output(a3 <- adapt.concept2.sFFLHD.R6$new(D=2,L=3,func=function(x)logistic_plateau(x[1])*logistic_plateau(x[2]), obj="desirability", des_func=des_func_grad_norm2_meaninv_plateau, alpha_des=1e2, n0=10, take_until_maxpvar_below=1, package="GauPro_kernel", design='sFFLHD', selection_method="max_des_red_all"))
a3$run(1)
```

## Batch 2

```{r bat32, echo=FALSE}
tmp <- capture.output(a3$run(1))
```

## Batch 3

```{r bat33, echo=FALSE}
tmp <- capture.output(a3$run(1))
```

## Batch 4

```{r bat34, echo=FALSE}
# tmp <- capture.output(a3$run(1))
```

## Batch 5

```{r bat35, echo=FALSE}
# tmp <- capture.output(a3$run(1))
```

## Batch 6

```{r bat36, echo=FALSE}
# tmp <- capture.output(a3$run(1))
```

## Batch 7

```{r bat37, echo=FALSE}
# tmp <- capture.output(a3$run(1))
```