---
title: "Meeting 10/18"
author: "Collin Erickson"
date: "October 18, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=TRUE)
setwd("..//") # Will get reset, but need this to have source below work properly
source("adaptconcept2_sFFLHD_R6.R")

logistic <- function(x, offset, scl) {1 / (1 + exp(-scl*(x-offset)))}; 
logistic_plateau <- function(x) {logistic(x[1], .15, 15) - logistic(x[1], .85,15)}; #curve(Vectorize(logistic_plateau)(x)); #cf(logistic_plateau)

```

## Plateau (bad form), nug=1e-4

```{r p1, echo=F, message=F}

# grad_norm2_meaninv_plateau
invisible(capture.output({set.seed(4); csa(); a <- adapt.concept2.sFFLHD.R6$new(D=1,L=3,func=Vectorize(logistic_plateau), obj="desirability", des_func=des_func_grad_norm2_meaninv_plateau, alpha_des=1, weight_const=0, n0=4, take_until_maxpvar_below=1, package="GauPro_kernel", design='sFFLHD', selection_method="max_des_red_all", nugget=1e-4); a$run(3, plotlastonly = T)}))
```

<a href="javascript:slidedeck.loadSlide(2)">Slide 2</a>
<a href="javascript:slidedeck.loadSlide(11)">Slide 11</a>
<a href="javascript:slidedeck.loadSlide(20)">Slide 20</a>
<a href="javascript:slidedeck.loadSlide(29)">Slide 29</a>
<a href="javascript:slidedeck.loadSlide(38)">Slide 38</a>

<!-- [Next test](#/1-D,-$E[g(x)^2]$,-no-$1+\alpha$,-single-logistic) -->



## Batch 6
```{r p6, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```

## Batch 9
```{r p9, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```

## Batch 12
```{r p12, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```

## Batch 15
```{r p15, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```

## Batch 18
```{r p18, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```

## Batch 21
```{r p21, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```

## Batch 24
```{r p24, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```

## Batch 27
```{r p27, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```


## 1-D, $E[g(x)^2]$, no $1+\alpha$, single logistic

```{r, echo=F, message=F}
invisible(capture.output({set.seed(2); csa(); a <- adapt.concept2.sFFLHD.R6$new(D=1,L=3,func=Vectorize(function(xx)logistic(xx,.5,15)), obj="desirability", des_func=des_func_grad_norm2_mean, alpha_des=1, weight_const = 0, n0=4, take_until_maxpvar_below=1, package="GauPro_kernel", design='sFFLHD', selection_method="max_des_red_all", nugget=1e-4); a$run(3, plotlastonly=T)}))
```


<a href="javascript:slidedeck.loadSlide(2)">Slide 2</a>
<a href="javascript:slidedeck.loadSlide(11)">Slide 11</a>
<a href="javascript:slidedeck.loadSlide(20)">Slide 20</a>
<a href="javascript:slidedeck.loadSlide(29)">Slide 29</a>
<a href="javascript:slidedeck.loadSlide(38)">Slide 38</a>



## Batch 6
```{r pq6, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```

## Batch 9
```{r pq9, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```

## Batch 12
```{r pq12, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```

## Batch 15
```{r pq15, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```

## Batch 18
```{r pq18, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```

## Batch 21
```{r pq21, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```

## Batch 24
```{r pq24, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```

## Batch 27
```{r pq27, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```



## 1-D, plateau (bad form), no $1+\alpha$, single logistic

```{r pqr3, echo=F, message=F}
invisible(capture.output({set.seed(2); csa(); a <- adapt.concept2.sFFLHD.R6$new(D=1,L=3,func=Vectorize(function(xx)logistic(xx,.5,15)), obj="desirability", des_func=des_func_grad_norm2_meaninv_plateau, alpha_des=1, weight_const = 0, n0=4, take_until_maxpvar_below=1, package="GauPro_kernel", design='sFFLHD', selection_method="max_des_red_all", nugget=1e-4); a$run(3, plotlastonly=T)}))
```

<a href="javascript:slidedeck.loadSlide(2)">Slide 2</a>
<a href="javascript:slidedeck.loadSlide(11)">Slide 11</a>
<a href="javascript:slidedeck.loadSlide(20)">Slide 20</a>
<a href="javascript:slidedeck.loadSlide(29)">Slide 29</a>
<a href="javascript:slidedeck.loadSlide(38)">Slide 38</a>

[Next test](#/1-D,-$E[g(x)^2]$,-no-$1+\alpha$,-single-logistic)



## Batch 6
```{r pqr6, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```


## Batch 9
```{r pqr9, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```

## Batch 12
```{r pqr12, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```

## Batch 15
```{r pqr15, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```

## Batch 18
```{r pqr18, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```

## Batch 21
```{r pqr21, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```

## Batch 24
```{r pqr24, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```

## Batch 27
```{r pqr27, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```



## 1-D, plateau (bad form), 1+10, single logistic

```{r pqrs3, echo=F, message=F}
invisible(capture.output({set.seed(2); csa(); a <- adapt.concept2.sFFLHD.R6$new(D=1,L=3,func=Vectorize(function(xx)logistic(xx,.5,15)), obj="desirability", des_func=des_func_grad_norm2_meaninv_plateau, alpha_des=10, weight_const = 1, n0=4, take_until_maxpvar_below=1, package="GauPro_kernel", design='sFFLHD', selection_method="max_des_red_all", nugget=1e-4); a$run(3, plotlastonly=T)}))
```

<a href="javascript:slidedeck.loadSlide(2)">Slide 2</a>
<a href="javascript:slidedeck.loadSlide(11)">Slide 11</a>
<a href="javascript:slidedeck.loadSlide(20)">Slide 20</a>
<a href="javascript:slidedeck.loadSlide(29)">Slide 29</a>
<a href="javascript:slidedeck.loadSlide(38)">Slide 38</a>

[Next test](#/1-D,-$E[g(x)^2]$,-no-$1+\alpha$,-single-logistic)



## Batch 6
```{r pqrs6, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```


## Batch 9
```{r pqrs9, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```

## Batch 12
```{r pqrs12, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```

## Batch 15
```{r pqrs15, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```

## Batch 18
```{r pqrs18, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```

## Batch 21
```{r pqrs21, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```

## Batch 24
```{r pqrs24, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```

## Batch 27
```{r pqrs27, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```






## 2-D, $E[g^2]$, no $1+\alpha$, $sin(2*pi*x[1]) + .5*sin(4*pi*x[1]) + x[2]^2$

```{r d3, echo=F, message=F}
invisible(capture.output({set.seed(2); csa(); a <- adapt.concept2.sFFLHD.R6$new(D=2,L=3,func=function(x) {sin(2*pi*x[1]) + .5*sin(4*pi*x[1]) +0*rnorm(1,0,.03) + x[2]^2}, obj="desirability", des_func=des_func_grad_norm2_mean, alpha_des=1, weight_const = 0, n0=6, take_until_maxpvar_below=1, package="GauPro_kernel", design='sFFLHD', selection_method="max_des_red_all", nugget=1e-5, verbose=0); a$run(3, plotlastonly=TRUE)}))
```

<a href="javascript:slidedeck.loadSlide(2)">Slide 2</a>
<a href="javascript:slidedeck.loadSlide(11)">Slide 11</a>
<a href="javascript:slidedeck.loadSlide(20)">Slide 20</a>
<a href="javascript:slidedeck.loadSlide(29)">Slide 29</a>
<a href="javascript:slidedeck.loadSlide(38)">Slide 38</a>

[Next test](#/1-D,-$E[g(x)^2]$,-no-$1+\alpha$,-single-logistic)



## Batch 6
```{r d6, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```


## Batch 9
```{r d9, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```




## 2-D, $E[g^2]$, no $1+\alpha$, double logistic

```{r de3, echo=F, message=F}
invisible(capture.output({set.seed(2); csa(); a <- adapt.concept2.sFFLHD.R6$new(D=2,L=3,func=logistic_plateau, obj="desirability", des_func=des_func_grad_norm2_mean, alpha_des=1, weight_const = 0, n0=6, take_until_maxpvar_below=1, package="GauPro_kernel", design='sFFLHD', selection_method="max_des_red_all", nugget=1e-5, verbose=0); a$run(3, plotlastonly=TRUE)}))
```

<a href="javascript:slidedeck.loadSlide(2)">Slide 2</a>
<a href="javascript:slidedeck.loadSlide(11)">Slide 11</a>
<a href="javascript:slidedeck.loadSlide(20)">Slide 20</a>
<a href="javascript:slidedeck.loadSlide(29)">Slide 29</a>
<a href="javascript:slidedeck.loadSlide(38)">Slide 38</a>




## Batch 6
```{r de6, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```


## Batch 9
```{r de9, echo=F, message=F}
invisible(capture.output(a$run(3, plotlastonly = T)))
```
