---
title: "Meeting 11/8 Example OTL Circuit"
author: "Collin Erickson"
date: "November 8, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=TRUE)
setwd("..//..//") # Will get reset, but need this to have source below work properly
source("adaptconcept2_sFFLHD_R6.R")
```



## Last week

* Not big difference when using $\alpha=$ 0, 0.5, 1 (esp last two)

* Want to test one at a time with grid of candidate points


```{r runfunc}
nruns <- 10
D <- 2
func <- vertigrad
actual_des_func <- actual_des_func_grad_norm2_mean_vertigrad #get_num_actual_des_func_grad_norm2_mean(logistic15)
n0 <- 3*D # 6 initial points
n_batches_to_run <- 12  # Gets up to 18+3*14=60=10*D
```



## OTL circuit, $E[g^2]$, $\alpha=1$, sFFLHD batch 3

```{r m1_runfunc}
m1_runfunc <- function() {
  adapt.concept2.sFFLHD.R6$new(D=D,L=3,func=func, obj="desirability", des_func=des_func_grad_norm2_mean, 
                               alpha_des=1, weight_const=0, take_until_maxpvar_below=1, 
                               package="laGP_GauPro_kernel", design='sFFLHD', 
                               selection_method="max_des_red_all", nugget=1e-6, 
                               actual_des_func=actual_des_func, 
                               verbose=0, nconsider=c(Inf,10,10), nconsider_random=c(0),
                               n0=n0
                               # X0=lhs::optimumLHS(n=6,k=2),
                               # Xopts=Xopts
                               )
}
m1_runs <- vector("list", nruns)
```


```{r m1e1, echo=F, message=F}
invisible(capture.output({set.seed(1); csa(); m1e1 <- m1_runfunc(); m1e1$run(n_batches_to_run, plotlastonly = T)}))
m1_runs[[1]] <- m1e1
```

## m1e2

```{r m1e2, echo=F, message=F}
i <- 2
invisible(capture.output({set.seed(i); csa(); m1e2 <- m1_runfunc(); m1e2$run(n_batches_to_run, plotlastonly = T)}))
m1_runs[[i]] <- m1e2
```

## m1e3

```{r m1e3, echo=F, message=F}
i <- 3
invisible(capture.output({set.seed(i); csa(); m1e3 <- m1_runfunc(); m1e3$run(n_batches_to_run, plotlastonly = T)}))
m1_runs[[i]] <- m1e3
```

## m1e4

```{r m1e4, echo=F, message=F}
i <- 4
invisible(capture.output({set.seed(i); csa(); m1e4 <- m1_runfunc(); m1e4$run(n_batches_to_run, plotlastonly = T)}))
m1_runs[[i]] <- m1e4
```

## m1e5

```{r m1e5, echo=F, message=F}
i <- 5
invisible(capture.output({set.seed(i); csa(); m1e5 <- m1_runfunc(); m1e5$run(n_batches_to_run, plotlastonly = T)}))
m1_runs[[i]] <- m1e5
```

## m1e6

```{r m1e6, echo=F, message=F}
i <- 6
invisible(capture.output({set.seed(i); csa(); m1e6 <- m1_runfunc(); m1e6$run(n_batches_to_run, plotlastonly = T)}))
m1_runs[[i]] <- m1e6
```

## m1e7

```{r m1e7, echo=F, message=F}
i <- 7
invisible(capture.output({set.seed(i); csa(); m1e7 <- m1_runfunc(); m1e7$run(n_batches_to_run, plotlastonly = T)}))
m1_runs[[i]] <- m1e7
```

## m1e8

```{r m1e8, echo=F, message=F}
i <- 8
invisible(capture.output({set.seed(i); csa(); m1e8 <- m1_runfunc(); m1e8$run(n_batches_to_run, plotlastonly = T)}))
m1_runs[[i]] <- m1e8
```

## m1e9

```{r m1e9, echo=F, message=F}
i <- 9
invisible(capture.output({set.seed(i); csa(); m1e9 <- m1_runfunc(); m1e9$run(n_batches_to_run, plotlastonly = T)}))
m1_runs[[i]] <- m1e9
```

## m1e10

```{r m1e10, echo=F, message=F}
i <- 10
invisible(capture.output({set.seed(i); csa(); m1e10 <- m1_runfunc(); m1e10$run(n_batches_to_run, plotlastonly = T)}))
m1_runs[[i]] <- m1e10
```



## OTL circuit, $E[g^2]$, $\alpha=0$, sFFLHD batch 3

```{r m2_runfunc}
m2_runfunc <- function() {
  adapt.concept2.sFFLHD.R6$new(D=D,L=3,func=func, obj="desirability", des_func=des_func_mean_grad_norm2, 
                               alpha_des=1, weight_const=0, take_until_maxpvar_below=1, 
                               package="laGP_GauPro_kernel", design='sFFLHD', 
                               selection_method="max_des_red_all", nugget=1e-6, 
                               actual_des_func=actual_des_func, 
                               verbose=0, nconsider=c(Inf,10,10), nconsider_random=c(0),
                               n0=n0
                               # X0=lhs::optimumLHS(n=6,k=2),
                               # Xopts=Xopts
                               )
}
m2_runs <- vector("list", nruns)
```


```{r m2e1, echo=F, message=F}
invisible(capture.output({set.seed(1); csa(); m2e1 <- m2_runfunc(); m2e1$run(n_batches_to_run, plotlastonly = T)}))
m2_runs[[1]] <- m2e1
```

```{r m2e2, echo=F, message=F}
# i <- 2
invisible(capture.output({set.seed(2); csa(); m2e2 <- m2_runfunc(); m2e2$run(n_batches_to_run, plotlastonly = T)}))
m2_runs[[2]] <- m2e2
# invisible(capture.output({set.seed(i); csa(); m2_runs[[i]] <- m2_runfunc(); m2_runs[[i]]$run(n_batches_to_run, plotlastonly = T)}))
```

```{r m2e3, echo=F, message=F}
invisible(capture.output({set.seed(3); csa(); m2e3 <- m2_runfunc(); m2e3$run(n_batches_to_run, plotlastonly = T)}))
m2_runs[[3]] <- m2e3
```

## m2e4

```{r m2e4, echo=F, message=F}
i <- 4
invisible(capture.output({set.seed(i); csa(); m2e4 <- m2_runfunc(); m2e4$run(n_batches_to_run, plotlastonly = T)}))
m2_runs[[i]] <- m2e4
```

## m2e5

```{r m2e5, echo=F, message=F}
i <- 5
invisible(capture.output({set.seed(i); csa(); m2e5 <- m2_runfunc(); m2e5$run(n_batches_to_run, plotlastonly = T)}))
m2_runs[[i]] <- m2e5
```

## m2e6

```{r m2e6, echo=F, message=F}
i <- 6
invisible(capture.output({set.seed(i); csa(); m2e6 <- m2_runfunc(); m2e6$run(n_batches_to_run, plotlastonly = T)}))
m2_runs[[i]] <- m2e6
```

## m2e7

```{r m2e7, echo=F, message=F}
i <- 7
invisible(capture.output({set.seed(i); csa(); m2e7 <- m2_runfunc(); m2e7$run(n_batches_to_run, plotlastonly = T)}))
m2_runs[[i]] <- m2e7
```

## m2e8

```{r m2e8, echo=F, message=F}
i <- 8
invisible(capture.output({set.seed(i); csa(); m2e8 <- m2_runfunc(); m2e8$run(n_batches_to_run, plotlastonly = T)}))
m2_runs[[i]] <- m2e8
```

## m2e9

```{r m2e9, echo=F, message=F}
i <- 9
invisible(capture.output({set.seed(i); csa(); m2e9 <- m2_runfunc(); m2e9$run(n_batches_to_run, plotlastonly = T)}))
m2_runs[[i]] <- m2e9
```

## m2e10

```{r m2e10, echo=F, message=F}
i <- 10
invisible(capture.output({set.seed(i); csa(); m2e10 <- m2_runfunc(); m2e10$run(n_batches_to_run, plotlastonly = T)}))
m2_runs[[i]] <- m2e10
```






## OTL circuit, $E[g^2]$, $\alpha=1$, LHS batch 3

```{r m3_runfunc}
m3_runfunc <- function() {
  adapt.concept2.sFFLHD.R6$new(D=D,L=3,func=func, obj="desirability", des_func=des_func_grad_norm2_mean, 
                               alpha_des=1, weight_const=0, take_until_maxpvar_below=1, 
                               package="laGP_GauPro_kernel", design='given', 
                               selection_method="max_des_red_all", nugget=1e-6, 
                               actual_des_func=actual_des_func, 
                               verbose=0, nconsider=c(Inf,10,10), nconsider_random=c(0),
                               # n0=n0
                               X0=MaxPro::MaxProLHD(n=D*3, p=D, itermax=1e3)$Design[sample(1:(D*3)),], #lhs::optimumLHS(n=6,k=2),
                               Xopts=MaxPro::MaxProLHD(n=D*30, p=D, itermax=1e3)$Design[sample(1:(D*30)),]
                               )
}
m3_runs <- vector("list", nruns)
```


```{r m3e1, echo=F, message=F}
invisible(capture.output({set.seed(1); csa(); m3e1 <- m3_runfunc(); m3e1$run(n_batches_to_run, plotlastonly = T)}))
m3_runs[[1]] <- m3e1
```

## m3e2

```{r m3e2, echo=F, message=F}
i <- 2
invisible(capture.output({set.seed(i); csa(); m3e2 <- m3_runfunc(); m3e2$run(n_batches_to_run, plotlastonly = T)}))
m3_runs[[i]] <- m3e2
```

## m3e3

```{r m3e3, echo=F, message=F}
i <- 3
invisible(capture.output({set.seed(i); csa(); m3e3 <- m3_runfunc(); m3e3$run(n_batches_to_run, plotlastonly = T)}))
m3_runs[[i]] <- m3e3
```

## m3e4

```{r m3e4, echo=F, message=F}
i <- 4
invisible(capture.output({set.seed(i); csa(); m3e4 <- m3_runfunc(); m3e4$run(n_batches_to_run, plotlastonly = T)}))
m3_runs[[i]] <- m3e4
```

## m3e5

```{r m3e5, echo=F, message=F}
i <- 5
invisible(capture.output({set.seed(i); csa(); m3e5 <- m3_runfunc(); m3e5$run(n_batches_to_run, plotlastonly = T)}))
m3_runs[[i]] <- m3e5
```

## m3e6

```{r m3e6, echo=F, message=F}
i <- 6
invisible(capture.output({set.seed(i); csa(); m3e6 <- m3_runfunc(); m3e6$run(n_batches_to_run, plotlastonly = T)}))
m3_runs[[i]] <- m3e6
```

## m3e7

```{r m3e7, echo=F, message=F}
i <- 7
invisible(capture.output({set.seed(i); csa(); m3e7 <- m3_runfunc(); m3e7$run(n_batches_to_run, plotlastonly = T)}))
m3_runs[[i]] <- m3e7
```

## m3e8

```{r m3e8, echo=F, message=F}
i <- 8
invisible(capture.output({set.seed(i); csa(); m3e8 <- m3_runfunc(); m3e8$run(n_batches_to_run, plotlastonly = T)}))
m3_runs[[i]] <- m3e8
```

## m3e9

```{r m3e9, echo=F, message=F}
i <- 9
invisible(capture.output({set.seed(i); csa(); m3e9 <- m3_runfunc(); m3e9$run(n_batches_to_run, plotlastonly = T)}))
m3_runs[[i]] <- m3e9
```

## m3e10

```{r m3e10, echo=F, message=F}
i <- 10
invisible(capture.output({set.seed(i); csa(); m3e10 <- m3_runfunc(); m3e10$run(n_batches_to_run, plotlastonly = T)}))
m3_runs[[i]] <- m3e10
```





## OTL circuit, $E[g^2]$, $\alpha=0$, LHS batch 3

```{r m4_runfunc}
m4_runfunc <- function() {
  adapt.concept2.sFFLHD.R6$new(D=D,L=3,func=func, obj="desirability", des_func=des_func_mean_grad_norm2, 
                               alpha_des=1, weight_const=0, take_until_maxpvar_below=1, 
                               package="laGP_GauPro_kernel", design='given', 
                               selection_method="max_des_red_all", nugget=1e-6, 
                               actual_des_func=actual_des_func, 
                               verbose=0, nconsider=c(Inf,10,10), nconsider_random=c(0),
                               # n0=n0
                               X0=MaxPro::MaxProLHD(n=D*3, p=D, itermax=1e3)$Design[sample(1:(D*3)),], #lhs::optimumLHS(n=6,k=2),
                               Xopts=MaxPro::MaxProLHD(n=D*30, p=D, itermax=1e3)$Design[sample(1:(D*30)),]
                               )
}
m4_runs <- vector("list", nruns)
```


```{r m4e1, echo=F, message=F}
invisible(capture.output({set.seed(1); csa(); m4e1 <- m4_runfunc(); m4e1$run(n_batches_to_run, plotlastonly = T)}))
m4_runs[[1]] <- m4e1
```

## m4e2

```{r m4e2, echo=F, message=F}
i <- 2
invisible(capture.output({set.seed(i); csa(); m4e2 <- m4_runfunc(); m4e2$run(n_batches_to_run, plotlastonly = T)}))
m4_runs[[i]] <- m4e2
```

## m4e3

```{r m4e3, echo=F, message=F}
i <- 3
invisible(capture.output({set.seed(i); csa(); m4e3 <- m4_runfunc(); m4e3$run(n_batches_to_run, plotlastonly = T)}))
m4_runs[[i]] <- m4e3
```

## m4e4

```{r m4e4, echo=F, message=F}
i <- 4
invisible(capture.output({set.seed(i); csa(); m4e4 <- m4_runfunc(); m4e4$run(n_batches_to_run, plotlastonly = T)}))
m4_runs[[i]] <- m4e4
```

## m4e5

```{r m4e5, echo=F, message=F}
i <- 5
invisible(capture.output({set.seed(i); csa(); m4e5 <- m4_runfunc(); m4e5$run(n_batches_to_run, plotlastonly = T)}))
m4_runs[[i]] <- m4e5
```

## m4e6

```{r m4e6, echo=F, message=F}
i <- 6
invisible(capture.output({set.seed(i); csa(); m4e6 <- m4_runfunc(); m4e6$run(n_batches_to_run, plotlastonly = T)}))
m4_runs[[i]] <- m4e6
```

## m4e7

```{r m4e7, echo=F, message=F}
i <- 7
invisible(capture.output({set.seed(i); csa(); m4e7 <- m4_runfunc(); m4e7$run(n_batches_to_run, plotlastonly = T)}))
m4_runs[[i]] <- m4e7
```

## m4e8

```{r m4e8, echo=F, message=F}
i <- 8
invisible(capture.output({set.seed(i); csa(); m4e8 <- m4_runfunc(); m4e8$run(n_batches_to_run, plotlastonly = T)}))
m4_runs[[i]] <- m4e8
```

## m4e9

```{r m4e9, echo=F, message=F}
i <- 9
invisible(capture.output({set.seed(i); csa(); m4e9 <- m4_runfunc(); m4e9$run(n_batches_to_run, plotlastonly = T)}))
m4_runs[[i]] <- m4e9
```

## m4e10

```{r m4e10, echo=F, message=F}
i <- 10
invisible(capture.output({set.seed(i); csa(); m4e10 <- m4_runfunc(); m4e10$run(n_batches_to_run, plotlastonly = T)}))
m4_runs[[i]] <- m4e10
```







## OTL circuit, $E[g^2]$, sFFLHD non-adaptive batch 3

```{r m5_runfunc}
m5_runfunc <- function() {
  adapt.concept2.sFFLHD.R6$new(D=D,L=3,func=func, obj="desirability", des_func=des_func_mean_grad_norm2, 
                               alpha_des=1, weight_const=0, take_until_maxpvar_below=1, 
                               package="laGP_GauPro_kernel", design='sFFLHD', 
                               selection_method="nonadapt", nugget=1e-6, 
                               actual_des_func=actual_des_func, 
                               verbose=0, nconsider=c(Inf,10,10), nconsider_random=c(0),
                               n0=n0
                               )
}
m5_runs <- vector("list", nruns)
```


```{r m5e1, echo=F, message=F}
invisible(capture.output({set.seed(1); csa(); m5e1 <- m5_runfunc(); m5e1$run(n_batches_to_run, plotlastonly = T)}))
m5_runs[[1]] <- m5e1
```

## m5e2

```{r m5e2, echo=F, message=F}
i <- 2
# invisible(capture.output({set.seed(i); csa(); m5e2 <- m5_runfunc(); m5e2$run(n_batches_to_run, plotlastonly = T)}))
# m5_runs[[i]] <- m5e2
invisible(capture.output({set.seed(i); csa(); m5_runs[[i]] <- m5_runfunc(); m5_runs[[i]]$run(n_batches_to_run, plotlastonly = T)}))
```

## m5e3

```{r m5e3, echo=F, message=F}
i <- 3
invisible(capture.output({set.seed(i); csa(); m5e3 <- m5_runfunc(); m5e3$run(n_batches_to_run, plotlastonly = T)}))
m5_runs[[i]] <- m5e3
```

## m5e4

```{r m5e4, echo=F, message=F}
i <- 4
invisible(capture.output({set.seed(i); csa(); m5e4 <- m5_runfunc(); m5e4$run(n_batches_to_run, plotlastonly = T)}))
m5_runs[[i]] <- m5e4
```

## m5e5

```{r m5e5, echo=F, message=F}
i <- 5
invisible(capture.output({set.seed(i); csa(); m5e5 <- m5_runfunc(); m5e5$run(n_batches_to_run, plotlastonly = T)}))
m5_runs[[i]] <- m5e5
```

## m5e6

```{r m5e6, echo=F, message=F}
i <- 6
invisible(capture.output({set.seed(i); csa(); m5e6 <- m5_runfunc(); m5e6$run(n_batches_to_run, plotlastonly = T)}))
m5_runs[[i]] <- m5e6
```

## m5e7

```{r m5e7, echo=F, message=F}
i <- 7
invisible(capture.output({set.seed(i); csa(); m5e7 <- m5_runfunc(); m5e7$run(n_batches_to_run, plotlastonly = T)}))
m5_runs[[i]] <- m5e7
```

## m5e8

```{r m5e8, echo=F, message=F}
i <- 8
invisible(capture.output({set.seed(i); csa(); m5e8 <- m5_runfunc(); m5e8$run(n_batches_to_run, plotlastonly = T)}))
m5_runs[[i]] <- m5e8
```

## m5e9

```{r m5e9, echo=F, message=F}
i <- 9
invisible(capture.output({set.seed(i); csa(); m5e9 <- m5_runfunc(); m5e9$run(n_batches_to_run, plotlastonly = T)}))
m5_runs[[i]] <- m5e9
```

## m5e10

```{r m5e10, echo=F, message=F}
i <- 10
invisible(capture.output({set.seed(i); csa(); m5e10 <- m5_runfunc(); m5e10$run(n_batches_to_run, plotlastonly = T)}))
m5_runs[[i]] <- m5e10
```



## OTL circuit, $E[g^2]$, sobel non-adaptive batch 3

```{r m6_runfunc}
m6_runfunc <- function() {
  adapt.concept2.sFFLHD.R6$new(D=D,L=3,func=func, obj="desirability", des_func=des_func_mean_grad_norm2, 
                               alpha_des=1, weight_const=0, take_until_maxpvar_below=1, 
                               package="laGP_GauPro_kernel", design='sobol', 
                               selection_method="nonadapt", nugget=1e-6, 
                               actual_des_func=actual_des_func, 
                               verbose=0, nconsider=c(Inf,10,10), nconsider_random=c(0),
                               n0=n0
  )
}
m6_runs <- vector("list", nruns)
```


```{r m6e1, echo=F, message=F}
invisible(capture.output({set.seed(1); csa(); m6e1 <- m6_runfunc(); m6e1$run(n_batches_to_run, plotlastonly = T)}))
m6_runs[[1]] <- m6e1
```

## m6e2

```{r m6e2, echo=F, message=F}
i <- 2
invisible(capture.output({set.seed(i); csa(); m6e2 <- m6_runfunc(); m6e2$run(n_batches_to_run, plotlastonly = T)}))
m6_runs[[i]] <- m6e2
# invisible(capture.output({set.seed(i); csa(); m6_runs[[i]] <- m6_runfunc(); m6_runs[[i]]$run(n_batches_to_run, plotlastonly = T)}))
```

## m6e3

```{r m6e3, echo=F, message=F}
i <- 3
invisible(capture.output({set.seed(i); csa(); m6e3 <- m6_runfunc(); m6e3$run(n_batches_to_run, plotlastonly = T)}))
m6_runs[[i]] <- m6e3
```

## m6e4

```{r m6e4, echo=F, message=F}
i <- 4
invisible(capture.output({set.seed(i); csa(); m6e4 <- m6_runfunc(); m6e4$run(n_batches_to_run, plotlastonly = T)}))
m6_runs[[i]] <- m6e4
```

## m6e5

```{r m6e5, echo=F, message=F}
i <- 5
invisible(capture.output({set.seed(i); csa(); m6e5 <- m6_runfunc(); m6e5$run(n_batches_to_run, plotlastonly = T)}))
m6_runs[[i]] <- m6e5
```

## m6e6

```{r m6e6, echo=F, message=F}
i <- 6
invisible(capture.output({set.seed(i); csa(); m6e6 <- m6_runfunc(); m6e6$run(n_batches_to_run, plotlastonly = T)}))
m6_runs[[i]] <- m6e6
```

## m6e7

```{r m6e7, echo=F, message=F}
i <- 7
invisible(capture.output({set.seed(i); csa(); m6e7 <- m6_runfunc(); m6e7$run(n_batches_to_run, plotlastonly = T)}))
m6_runs[[i]] <- m6e7
```

## m6e8

```{r m6e8, echo=F, message=F}
i <- 8
invisible(capture.output({set.seed(i); csa(); m6e8 <- m6_runfunc(); m6e8$run(n_batches_to_run, plotlastonly = T)}))
m6_runs[[i]] <- m6e8
```

## m6e9

```{r m6e9, echo=F, message=F}
i <- 9
invisible(capture.output({set.seed(i); csa(); m6e9 <- m6_runfunc(); m6e9$run(n_batches_to_run, plotlastonly = T)}))
m6_runs[[i]] <- m6e9
```

## m6e10

```{r m6e10, echo=F, message=F}
i <- 10
invisible(capture.output({set.seed(i); csa(); m6e10 <- m6_runfunc(); m6e10$run(n_batches_to_run, plotlastonly = T)}))
m6_runs[[i]] <- m6e10
```



## OTL circuit, $E[g^2]$, sFFLHD picking max SE batch 3

```{r m7_runfunc}
m7_runfunc <- function() {
  adapt.concept2.sFFLHD.R6$new(D=D,L=3,func=func, obj="desirability", des_func=des_func_mean_grad_norm2, 
                               alpha_des=1, weight_const=0, take_until_maxpvar_below=1, 
                               package="laGP_GauPro_kernel", design='sFFLHD', 
                               selection_method="ALM", nugget=1e-6, 
                               actual_des_func=actual_des_func, 
                               verbose=0, nconsider=c(Inf,10,10), nconsider_random=c(0),
                               n0=n0
  )
}
m7_runs <- vector("list", nruns)
```


```{r m7e1, echo=F, message=F}
invisible(capture.output({set.seed(1); csa(); m7e1 <- m7_runfunc(); m7e1$run(n_batches_to_run, plotlastonly = T)}))
m7_runs[[1]] <- m7e1
```

## m7e2

```{r m7e2, echo=F, message=F}
i <- 2
# invisible(capture.output({set.seed(i); csa(); m7e2 <- m7_runfunc(); m7e2$run(n_batches_to_run, plotlastonly = T)}))
# m7_runs[[i]] <- m7e2
invisible(capture.output({set.seed(i); csa(); m7_runs[[i]] <- m7_runfunc(); m7_runs[[i]]$run(n_batches_to_run, plotlastonly = T)}))
```

## m7e3

```{r m7e3, echo=F, message=F}
i <- 3
invisible(capture.output({set.seed(i); csa(); m7e3 <- m7_runfunc(); m7e3$run(n_batches_to_run, plotlastonly = T)}))
m7_runs[[i]] <- m7e3
```

## m7e4

```{r m7e4, echo=F, message=F}
i <- 4
invisible(capture.output({set.seed(i); csa(); m7e4 <- m7_runfunc(); m7e4$run(n_batches_to_run, plotlastonly = T)}))
m7_runs[[i]] <- m7e4
```

## m7e5

```{r m7e5, echo=F, message=F}
i <- 5
invisible(capture.output({set.seed(i); csa(); m7e5 <- m7_runfunc(); m7e5$run(n_batches_to_run, plotlastonly = T)}))
m7_runs[[i]] <- m7e5
```

## m7e6

```{r m7e6, echo=F, message=F}
i <- 6
invisible(capture.output({set.seed(i); csa(); m7e6 <- m7_runfunc(); m7e6$run(n_batches_to_run, plotlastonly = T)}))
m7_runs[[i]] <- m7e6
```

## m7e7

```{r m7e7, echo=F, message=F}
i <- 7
invisible(capture.output({set.seed(i); csa(); m7e7 <- m7_runfunc(); m7e7$run(n_batches_to_run, plotlastonly = T)}))
m7_runs[[i]] <- m7e7
```

## m7e8

```{r m7e8, echo=F, message=F}
i <- 8
invisible(capture.output({set.seed(i); csa(); m7e8 <- m7_runfunc(); m7e8$run(n_batches_to_run, plotlastonly = T)}))
m7_runs[[i]] <- m7e8
```

## m7e9

```{r m7e9, echo=F, message=F}
i <- 9
invisible(capture.output({set.seed(i); csa(); m7e9 <- m7_runfunc(); m7e9$run(n_batches_to_run, plotlastonly = T)}))
m7_runs[[i]] <- m7e9
```

## m7e10

```{r m7e10, echo=F, message=F}
i <- 10
invisible(capture.output({set.seed(i); csa(); m7e10 <- m7_runfunc(); m7e10$run(n_batches_to_run, plotlastonly = T)}))
m7_runs[[i]] <- m7e10
```



## OTL circuit, $E[g^2]$, sFFLHD picking max SE red batch 3

```{r m8_runfunc}
m8_runfunc <- function() {
  adapt.concept2.sFFLHD.R6$new(D=D,L=3,func=func, obj="desirability", des_func=des_func_mean_grad_norm2, 
                               alpha_des=1, weight_const=0, take_until_maxpvar_below=1, 
                               package="laGP_GauPro_kernel", design='sFFLHD', 
                               selection_method="ALC", nugget=1e-6, 
                               actual_des_func=actual_des_func, 
                               verbose=0, nconsider=c(Inf,10,10), nconsider_random=c(0),
                               n0=n0
  )
}
m8_runs <- vector("list", nruns)
```


```{r m8e1, echo=F, message=F}
invisible(capture.output({set.seed(1); csa(); m8e1 <- m8_runfunc(); m8e1$run(n_batches_to_run, plotlastonly = T)}))
m8_runs[[1]] <- m8e1
```

## m8e2

```{r m8e2, echo=F, message=F}
i <- 2
# invisible(capture.output({set.seed(i); csa(); m8e2 <- m8_runfunc(); m8e2$run(n_batches_to_run, plotlastonly = T)}))
# m8_runs[[i]] <- m8e2
invisible(capture.output({set.seed(i); csa(); m8_runs[[i]] <- m8_runfunc(); m8_runs[[i]]$run(n_batches_to_run, plotlastonly = T)}))
```

## m8e3

```{r m8e3, echo=F, message=F}
i <- 3
invisible(capture.output({set.seed(i); csa(); m8e3 <- m8_runfunc(); m8e3$run(n_batches_to_run, plotlastonly = T)}))
m8_runs[[i]] <- m8e3
```

## m8e4

```{r m8e4, echo=F, message=F}
i <- 4
invisible(capture.output({set.seed(i); csa(); m8e4 <- m8_runfunc(); m8e4$run(n_batches_to_run, plotlastonly = T)}))
m8_runs[[i]] <- m8e4
```

## m8e5

```{r m8e5, echo=F, message=F}
i <- 5
invisible(capture.output({set.seed(i); csa(); m8e5 <- m8_runfunc(); m8e5$run(n_batches_to_run, plotlastonly = T)}))
m8_runs[[i]] <- m8e5
```

## m8e6

```{r m8e6, echo=F, message=F}
i <- 6
invisible(capture.output({set.seed(i); csa(); m8e6 <- m8_runfunc(); m8e6$run(n_batches_to_run, plotlastonly = T)}))
m8_runs[[i]] <- m8e6
```

## m8e7

```{r m8e7, echo=F, message=F}
i <- 7
invisible(capture.output({set.seed(i); csa(); m8e7 <- m8_runfunc(); m8e7$run(n_batches_to_run, plotlastonly = T)}))
m8_runs[[i]] <- m8e7
```

## m8e8

```{r m8e8, echo=F, message=F}
i <- 8
invisible(capture.output({set.seed(i); csa(); m8e8 <- m8_runfunc(); m8e8$run(n_batches_to_run, plotlastonly = T)}))
m8_runs[[i]] <- m8e8
```

## m8e9

```{r m8e9, echo=F, message=F}
i <- 9
invisible(capture.output({set.seed(i); csa(); m8e9 <- m8_runfunc(); m8e9$run(n_batches_to_run, plotlastonly = T)}))
m8_runs[[i]] <- m8e9
```

## m8e10

```{r m8e10, echo=F, message=F}
i <- 10
invisible(capture.output({set.seed(i); csa(); m8e10 <- m8_runfunc(); m8e10$run(n_batches_to_run, plotlastonly = T)}))
m8_runs[[i]] <- m8e10
```





## Gather results

```{r gatherresultsm1, cache=F}
m1_stats <- data.frame()
for (i in 1:length(m1_runs)) {
  if (!is.null(m1_runs[[i]])) {
    m1_stats <- rbind(m1_stats, 
                      data.frame(m=1, rp=i, name="sWb3a1",
                                 iter=m1_runs[[i]]$stats$iter, 
                                 actual_intwerror=m1_runs[[i]]$stats$actual_intwerror, 
                                 mse=m1_runs[[i]]$stats$mse))
    }
}
m1_stats
```

```{r gatherresultsm2, cache=F}
m2_stats <- data.frame()
for (i in 1:length(m2_runs)) {
  if (!is.null(m2_runs[[i]])) {
    m2_stats <- rbind(m2_stats, 
                      data.frame(m=2, rp=i, name="sWb3a0",
                                 iter=m2_runs[[i]]$stats$iter, 
                                 actual_intwerror=m2_runs[[i]]$stats$actual_intwerror, 
                                 mse=m2_runs[[i]]$stats$mse))
    }
}
m2_stats
```

```{r gatherresultsm3, cache=F}
m3_stats <- data.frame()
for (i in 1:length(m3_runs)) {
  if (!is.null(m3_runs[[i]])) {
    m3_stats <- rbind(m3_stats, 
                      data.frame(m=3, rp=i, name="LWb3a1",
                                 iter=m3_runs[[i]]$stats$iter, 
                                 actual_intwerror=m3_runs[[i]]$stats$actual_intwerror, 
                                 mse=m3_runs[[i]]$stats$mse))
    }
}
m3_stats
```

```{r gatherresultsm4, cache=F}
m4_stats <- data.frame()
for (i in 1:length(m4_runs)) {
  if (!is.null(m4_runs[[i]])) {
    m4_stats <- rbind(m4_stats, 
                      data.frame(m=4, rp=i, name="LWb3a0",
                                 iter=m4_runs[[i]]$stats$iter, 
                                 actual_intwerror=m4_runs[[i]]$stats$actual_intwerror, 
                                 mse=m4_runs[[i]]$stats$mse))
    }
}
m4_stats
```

```{r gatherresultsm5, cache=F}
m5_stats <- data.frame()
for (i in 1:length(m5_runs)) {
  if (!is.null(m5_runs[[i]])) {
    m5_stats <- rbind(m5_stats, 
                      data.frame(m=5, rp=i, name="s",
                                 iter=m5_runs[[i]]$stats$iter, 
                                 actual_intwerror=m5_runs[[i]]$stats$actual_intwerror, 
                                 mse=m5_runs[[i]]$stats$mse))
    }
}
m5_stats
```

```{r gatherresultsm6, cache=F}
m6_stats <- data.frame()
for (i in 1:length(m6_runs)) {
  if (!is.null(m6_runs[[i]])) {
    m6_stats <- rbind(m6_stats, 
                      data.frame(m=6, rp=i, name="sobol",
                                 iter=m6_runs[[i]]$stats$iter, 
                                 actual_intwerror=m6_runs[[i]]$stats$actual_intwerror, 
                                 mse=m6_runs[[i]]$stats$mse))
  }
}
m6_stats
```

```{r gatherresultsm7, cache=F}
m7_stats <- data.frame()
for (i in 1:length(m7_runs)) {
  if (!is.null(m7_runs[[i]])) {
    m7_stats <- rbind(m7_stats, 
                      data.frame(m=7, rp=i, name="sALM",
                                 iter=m7_runs[[i]]$stats$iter, 
                                 actual_intwerror=m7_runs[[i]]$stats$actual_intwerror, 
                                 mse=m7_runs[[i]]$stats$mse))
  }
}
m7_stats
```


```{r gatherresultsm8, cache=F}
m8_stats <- data.frame()
for (i in 1:length(m8_runs)) {
  if (!is.null(m8_runs[[i]])) {
    m8_stats <- rbind(m8_stats, 
                      data.frame(m=8, rp=i, name="sALC",
                                 iter=m8_runs[[i]]$stats$iter, 
                                 actual_intwerror=m8_runs[[i]]$stats$actual_intwerror, 
                                 mse=m8_runs[[i]]$stats$mse))
  }
}
m8_stats
```

```{r gatherresults, cache=F}
m_stats <- rbind(m1_stats, m2_stats, m3_stats, m4_stats, m5_stats, m6_stats, m7_stats, m8_stats)
```




## Comparison of IntWerror

```{r plotintwerror_iwe, cache=F}
library(ggplot2) # , shape=as.factor(rp)
ggplot(data=m_stats, aes(x=iter, y=actual_intwerror, group=interaction(rp,name), color=name)) + geom_line() + geom_point()  + scale_y_continuous(trans='log10') #+ 
  #scale_color_hue(labels=expression(alpha==1,alpha==0,alpha==0.5,random))
```


## Weighted error by group

```{r plotawegroup, cache=F}
base_breaks <- function(n = 10){
  function(x) {
    axisTicks(log10(range(x, na.rm = TRUE)), log = TRUE, n = n)
  }
}
p1 <- ggplot(data=m_stats[m_stats$iter==max(m_stats$iter),], 
           aes(x=name, y=actual_intwerror, colour = name)
    )# +  geom_jitter(width=.1)
p1 <- p1 + geom_boxplot()
p1 <- p1 + geom_jitter(width=.1)
p1 <- p1 + #scale_y_log10() + 
  scale_y_continuous(trans="log", breaks = base_breaks())
# p1 <- p1 + scale_color_hue(labels=c('alpha=1','alpha=0','alpha=.5','nonadapt'))
p1
```



## Comparison of mse

```{r plotintwerror_mse, cache=F}
library(ggplot2) # , shape=as.factor(rp)
ggplot(data=m_stats, aes(x=iter, y=mse, group=interaction(rp,name), color=name)) + geom_line() + geom_point()  + scale_y_continuous(trans='log10') #+ 
  #scale_color_hue(labels=expression(alpha==1,alpha==0,alpha==0.5,random))
```

## MSE by group

```{r plotmsegroup, cache=F}
base_breaks <- function(n = 10){
  function(x) {
    axisTicks(log10(range(x, na.rm = TRUE)), log = TRUE, n = n)
  }
}
p1 <- ggplot(data=m_stats[m_stats$iter==max(m_stats$iter),], 
           aes(x=name, y=mse, colour = name)
    )# +  geom_jitter(width=.1)
p1 <- p1 + geom_boxplot()
p1 <- p1 + geom_jitter(width=.1)
p1 <- p1 + #scale_y_log10() + 
  scale_y_continuous(trans="log", breaks = base_breaks())
# p1 <- p1 + scale_color_hue(labels=c('alpha=1','alpha=0','alpha=.5','nonadapt'))
p1
```