---
title: "Stochastic Lanchester Tests 2"
author: "Collin Erickson"
date: "May 29, 2018"
output: ioslides_presentation
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- <style type="text/css"> -->
<!-- .main-container { -->
<!--   max-width: 1800px; -->
<!--   margin-left: auto; -->
<!--   margin-right: auto; -->
<!-- } -->
<!-- </style> -->

## Set up

```{r, message=FALSE}
# Need to be up folder to source file
setwd(".//..//..")
source('C://Users//cbe117//Documents//GitHub//DOE-code///adaptconcept2_sFFLHD_R6.R')
```


## Region 5


```{r}
datafilename5 <- ".//..//LanchesterDataFiles//output_200K_region5.csv"
datadf5 <- read.csv(datafilename5)

datafunction5 <- function(x, outputcolumn=11) {
  # cat(x, "\n")
  which.ind <- which(c(apply(datadf5, 1, function(rr) {(all(abs(x-rr[1:4])<1e-8))})))
  if (length(which.ind) != 1) {
    browser("Not exactly one indice that matches")
  }
  datadf5[which.ind, outputcolumn]
}
x1 <- as.numeric(datadf5[8,1:4])
datafunction5(x1)
```

```{r}
names(datadf5)
```

## Battle duration


```{r}
summary(datadf5[,13])
```


```{r}
pairs(datadf5[,c(1:4,13)])
```


<!-- # ```{r 5_dur, cache=TRUE, out.width='.49\\linewidth', fig.width=4, fig.height=4,fig.show='hold',fig.align='center'} -->
<!--```{r 5_dur, cache=TRUE, out.width="49%", fig.align='center', fig.show='hold', fig.width=6, fig.height=6}-->
```{r}
# ignore
set.seed(1); csa(); a <- adapt.concept2.sFFLHD.R6$new(
  D=4,L=4, design_seed=6562780, func=function(x)datafunction5(x,outputcolumn=13), func_fast = F,
  nugget = 1e-3,estimate.nugget = F,
  obj="desirability", des_func=des_func_grad_norm2_mean,
  actual_des_func=NULL,#get_num_actual_des_func_grad_norm2_mean(),
  stage1batches=2, alpha_des=1, weight_const=0,
  package="laGP_GauPro_kernel", design='sFFLHD',
  error_power=2,
  selection_method="max_des_red_all_best"
  # selection_method="ALC_all_best"
)
a$run(12, plotlastonly=T)
```

## Mean prediction at midpoint

```{r}
cf_highdim(a$mod$predict, D=4, pts=a$X, batchmax=Inf)
```

## Mean prediction averaged out

```{r}
cf_highdim(a$mod$predict, D=4, pts=a$X, batchmax=Inf, average=T)

```

## Weight prediction at midpoint

```{r}
cf_highdim(a$mod$mod.extra$GauPro$mod$grad_norm2_mean, 4, average=F, average_reps = 1e2, n=8, batchmax=Inf, pts=a$X)
```

## Weight prediction averaged out

```{r}
cf_highdim(a$mod$mod.extra$GauPro$mod$grad_norm2_mean, 4, average=T, average_reps = 1e2, n=8, batchmax=Inf, pts=a$X)
# rm(a)
```

## ler Loss Exchange Ratio

```{r}
summary(datadf5[,15])
```



```{r}
pairs(datadf5[,c(1:4,15)])
```

## ler

```{r 5_ler}
set.seed(1); csa(); a <- adapt.concept2.sFFLHD.R6$new(
  D=4,L=4, design_seed=6562780, func=function(x)datafunction5(x,outputcolumn=15), func_fast = F,
  nugget = 1e-3,estimate.nugget = F,
  obj="desirability", des_func=des_func_grad_norm2_mean,
  actual_des_func=NULL,#get_num_actual_des_func_grad_norm2_mean(),
  stage1batches=2, alpha_des=1, weight_const=0,
  package="laGP_GauPro_kernel", design='sFFLHD',
  error_power=2,
  selection_method="max_des_red_all_best"
  # selection_method="ALC_all_best"
)
a$run(12, plotlastonly=T)
# cf_highdim(a$mod$predict, D=4, pts=a$X)
# rm(a)
```



## Mean prediction at midpoint

```{r}
cf_highdim(a$mod$predict, D=4, pts=a$X, batchmax=Inf)
```

## Mean prediction averaged out

```{r}
cf_highdim(a$mod$predict, D=4, pts=a$X, batchmax=Inf, average=T)
```

## Weight prediction at midpoint

```{r}
cf_highdim(a$mod$mod.extra$GauPro$mod$grad_norm2_mean, 4,average=F, average_reps = 1e2, n=8, batchmax=Inf, pts=a$X)
```

## Weight prediction averaged out

```{r}
cf_highdim(a$mod$mod.extra$GauPro$mod$grad_norm2_mean, 4, average=T, average_reps = 1e2, n=8, batchmax=Inf, pts=a$X)
# rm(a)
```



## recip ler Reciprocal Loss Exchange Ratio

```{r}
pairs(datadf5[,c(1:4,17)])
```

## rler

```{r 5_rler, cache=TRUE}
set.seed(1); csa(); rler5 <- adapt.concept2.sFFLHD.R6$new(
  D=4,L=4, design_seed=6562780, func=function(x)datafunction5(x,outputcolumn=17), func_fast = F,
  nugget = 1e-6,estimate.nugget = F,
  obj="desirability", des_func=des_func_grad_norm2_mean,
  actual_des_func=NULL,#get_num_actual_des_func_grad_norm2_mean(),
  stage1batches=2, alpha_des=1, weight_const=0,
  package="laGP_GauPro_kernel", design='sFFLHD',
  error_power=2,
  selection_method="max_des_red_all_best"
  # selection_method="ALC_all_best"
)
rler5$run(12, plotlastonly=T)
# cf_highdim(rler5$mod$predict, D=4, pts=rler5$X, batchmax=Inf)

```

```{r}
c(
  rler5$mod$mod.extra$GauPro$mod$nug,
  rler5$mod$mod.extra$GauPro$mod$s2_hat,
  rler5$mod$mod.extra$GauPro$mod$nug * 
  rler5$mod$mod.extra$GauPro$mod$s2_hat
)
```

## Mean at midpoint

```{r}
cf_highdim(rler5$mod$predict, D=4, pts=rler5$X, batchmax=Inf)
```


## Mean, averaged over 2 dims

```{r plotmeanaveraged}
cf_highdim(rler5$mod$predict, D=4, pts=rler5$X, average=TRUE, batchmax=Inf, average_reps=1e2, n=10)
```

## Weight prediction at midpoint

```{r plotweight}
cf_highdim(rler5$mod$mod.extra$GauPro$mod$grad_norm2_mean, 4, average=F, average_reps = 1e2, n=8, batchmax=Inf, pts=rler5$X)
```

## Weight prediction averaged out

```{r plotweightaveraged}
cf_highdim(rler5$mod$mod.extra$GauPro$mod$grad_norm2_mean, 4, average=T, average_reps = 1e2, n=8, batchmax=Inf, pts=rler5$X)
```



