---
title: "Meeting 11/8 Example 4 vertigrad"
author: "Collin Erickson"
date: "November 8, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=TRUE)
setwd("..//..//") # Will get reset, but need this to have source below work properly
source("adaptconcept2_sFFLHD_R6.R")
```



## Last week

* Not big difference when using $\alpha=$ 0, 0.5, 1 (esp last two)

* Want to test one at a time with grid of candidate points


```{r runfunc}
ncd <- 10
Xopts <- as.matrix(reshape::expand.grid.df(data.frame(a=0:ncd),data.frame(b=0:ncd)))[sample(1:(ncd+1)^2),]/ncd
runfunc <- function(des_func, selection_method="max_des_red_all") {
  adapt.concept2.sFFLHD.R6$new(D=2,L=1,func=vertigrad, obj="desirability", des_func=des_func, 
                               alpha_des=1, weight_const=0, take_until_maxpvar_below=1, 
                               package="laGP_GauPro_kernel", design='given', 
                               selection_method=selection_method, nugget=1e-6, 
                               actual_des_func=actual_des_func_grad_norm2_mean_vertigrad, 
                               verbose=0, nconsider=c(Inf,10,10), nconsider_random=c(0),
                               X0=lhs::optimumLHS(n=6,k=2),
                               Xopts=Xopts
                               )
}
```



## Vertigrad, $E[g^2]$, $\alpha=1$

```{r m1e1, echo=F, message=F}
invisible(capture.output({set.seed(5); csa(); m1e1 <- runfunc(des_func=des_func_grad_norm2_mean); m1e1$run(3, plotlastonly = T)}))
```

## Batch 6 $\alpha=1$
```{r m1e1_2, echo=F, message=F}
invisible(capture.output(m1e1_2 <- m1e1$run(3, plotlastonly = T)))
```


## Batch 9 $\alpha=1$
```{r m1e1_3, echo=F, message=F}
invisible(capture.output(m1e1_3 <- m1e1_2$run(3, plotlastonly = T)))
```

## Batch 12 $\alpha=1$
```{r m1e1_4, echo=F, message=F}
invisible(capture.output(m1e1_4 <- m1e1_3$run(3, plotlastonly = T)))
```

## Batch 15 $\alpha=1$
```{r m1e1_5, echo=F, message=F}
invisible(capture.output(m1e1_5 <- m1e1_4$run(3, plotlastonly = T)))
```

## Batch 18 $\alpha=1$
```{r m1e1_6, echo=F, message=F}
invisible(capture.output(m1e1_6 <- m1e1_5$run(3, plotlastonly = T)))
```

## Batch 21 $\alpha=1$
```{r m1e1_7, echo=F, message=F}
invisible(capture.output(m1e1_7 <- m1e1_6$run(3, plotlastonly = T)))
```

## Batch 24 $\alpha=1$
```{r m1e1_8, echo=F, message=F}
invisible(capture.output(m1e1_8 <- m1e1_7$run(3, plotlastonly = T)))
```

## Batch 27 $\alpha=1$
```{r m1e1_9, echo=F, message=F}
invisible(capture.output(m1e1_9 <- m1e1_8$run(3, plotlastonly = T)))
```

## Batch 30 $\alpha=1$
```{r m1e1_10, echo=F, message=F}
invisible(capture.output(m1e1_10 <- m1e1_9$run(3, plotlastonly = T)))
```

## Point order
```{r po1}
plot(NULL, xlim=c(0,1), ylim=c(0,1))
text(m1e1_10$X, labels=m1e1_10$X_tracker$iteration_added)
```




## Vertigrad, $E[g]^2$ $\alpha=0$

```{r m2e1, echo=F, message=F}
invisible(capture.output({set.seed(5); csa(); m2e1 <- runfunc(des_func=des_func_mean_grad_norm2); m2e1$run(3, plotlastonly = T)}))
```

## Batch 6 $\alpha=0$
```{r m2e1_2, echo=F, message=F}
invisible(capture.output(m2e1_2 <- m2e1$run(3, plotlastonly = T)))
```

## Batch 9 $\alpha=0$
```{r m2e1_3, echo=F, message=F}
invisible(capture.output(m2e1_3 <- m2e1_2$run(3, plotlastonly = T)))
```

## Batch 12 $\alpha=0$
```{r m2e1_4, echo=F, message=F}
invisible(capture.output(m2e1_4 <- m2e1_3$run(3, plotlastonly = T)))
```

## Batch 15 $\alpha=0$
```{r m2e1_5, echo=F, message=F}
invisible(capture.output(m2e1_5 <- m2e1_4$run(3, plotlastonly = T)))
```

## Batch 18 $\alpha=0$
```{r m2e1_6, echo=F, message=F}
invisible(capture.output(m2e1_6 <- m2e1_5$run(3, plotlastonly = T)))
```

## Batch 21 $\alpha=0$
```{r m2e1_7, echo=F, message=F}
invisible(capture.output(m2e1_7 <- m2e1_6$run(3, plotlastonly = T)))
```

## Batch 24 $\alpha=0$
```{r m2e1_8, echo=F, message=F}
invisible(capture.output(m2e1_8 <- m2e1_7$run(3, plotlastonly = T)))
```

## Batch 27 $\alpha=0$
```{r m2e1_9, echo=F, message=F}
invisible(capture.output(m2e1_9 <- m2e1_8$run(3, plotlastonly = T)))
```

## Batch 30 $\alpha=0$
```{r m2e1_10, echo=F, message=F}
invisible(capture.output(m2e1_10 <- m2e1_9$run(3, plotlastonly = T)))
```

## Point order
```{r po2}
plot(NULL, xlim=c(0,1), ylim=c(0,1))
text(m2e1_10$X, labels=m2e1_10$X_tracker$iteration_added)
```


## Vertigrad, $E[g]^2 + 0.5 E[r^Tr]$,  $\alpha=0.5$

```{r m3e1, echo=F, message=F}
invisible(capture.output({set.seed(5); csa(); m3e1 <- runfunc(des_func=get_des_func_grad_norm2_mean_alpha(alpha=.5)); m3e1$run(3, plotlastonly = T)}))
```

## Batch 6 $\alpha=0.5$
```{r m3e1_2, echo=F, message=F}
invisible(capture.output(m3e1_2 <- m3e1$run(3, plotlastonly = T)))
```

## Batch 9 $\alpha=0.5$
```{r m3e1_3, echo=F, message=F}
invisible(capture.output(m3e1_3 <- m3e1_2$run(3, plotlastonly = T)))
```

## Batch 12 $\alpha=0.5$
```{r m3e1_4, echo=F, message=F}
invisible(capture.output(m3e1_4 <- m3e1_3$run(3, plotlastonly = T)))
```

## Batch 15 $\alpha=0.5$
```{r m3e1_5, echo=F, message=F}
invisible(capture.output(m3e1_5 <- m3e1_4$run(3, plotlastonly = T)))
```

## Batch 18 $\alpha=0.5$
```{r m3e1_6, echo=F, message=F}
invisible(capture.output(m3e1_6 <- m3e1_5$run(3, plotlastonly = T)))
```

## Batch 21 $\alpha=0.5$
```{r m3e1_7, echo=F, message=F}
invisible(capture.output(m3e1_7 <- m3e1_6$run(3, plotlastonly = T)))
```

## Batch 24 $\alpha=0.5$
```{r m3e1_8, echo=F, message=F}
invisible(capture.output(m3e1_8 <- m3e1_7$run(3, plotlastonly = T)))
```

## Batch 27 $\alpha=0.5$
```{r m3e1_9, echo=F, message=F}
invisible(capture.output(m3e1_9 <- m3e1_8$run(3, plotlastonly = T)))
```

## Batch 30 $\alpha=0.5$
```{r m3e1_10, echo=F, message=F}
invisible(capture.output(m3e1_10 <- m3e1_9$run(3, plotlastonly = T)))
```

## Point order
```{r po3}
plot(NULL, xlim=c(0,1), ylim=c(0,1))
text(m3e1_10$X, labels=m3e1_10$X_tracker$iteration_added)
```



## Vertigrad, random

```{r m4e1, echo=F, message=F}
invisible(capture.output({set.seed(5); csa(); m4e1 <- runfunc(des_func=des_func_grad_norm2_mean, selection_method="nonadapt"); m4e1$run(3, plotlastonly = T)}))
```

## Batch 6 random
```{r m4e1_2, echo=F, message=F}
invisible(capture.output(m4e1_2 <- m4e1$run(3, plotlastonly = T)))
```

## Batch 9 random
```{r m4e1_3, echo=F, message=F}
invisible(capture.output(m4e1_3 <- m4e1_2$run(3, plotlastonly = T)))
```

## Batch 12 random
```{r m4e1_4, echo=F, message=F}
invisible(capture.output(m4e1_4 <- m4e1_3$run(3, plotlastonly = T)))
```

## Batch 15 random
```{r m4e1_5, echo=F, message=F}
invisible(capture.output(m4e1_5 <- m4e1_4$run(3, plotlastonly = T)))
```

## Batch 18 random
```{r m4e1_6, echo=F, message=F}
invisible(capture.output(m4e1_6 <- m4e1_5$run(3, plotlastonly = T)))
```

## Batch 21 random
```{r m4e1_7, echo=F, message=F}
invisible(capture.output(m4e1_7 <- m4e1_6$run(3, plotlastonly = T)))
```

## Batch 24 random
```{r m4e1_8, echo=F, message=F}
invisible(capture.output(m4e1_8 <- m4e1_7$run(3, plotlastonly = T)))
```

## Batch 27 random
```{r m4e1_9, echo=F, message=F}
invisible(capture.output(m4e1_9 <- m4e1_8$run(3, plotlastonly = T)))
```

## Batch 30 random
```{r m4e1_10, echo=F, message=F}
invisible(capture.output(m4e1_10 <- m4e1_9$run(3, plotlastonly = T)))
```

## Point order
```{r po4}
plot(NULL, xlim=c(0,1), ylim=c(0,1))
text(m4e1_10$X, labels=m4e1_10$X_tracker$iteration_added)
```




## Point order
```{r po_all, fig.width=3, fig.height=3, fig.show='hold'}
plot(NULL, xlim=c(0,1), ylim=c(0,1), main="alpha=1"); text(m1e1_10$X, labels=m1e1_10$X_tracker$iteration_added)
plot(NULL, xlim=c(0,1), ylim=c(0,1), main="alpha=0"); text(m2e1_10$X, labels=m2e1_10$X_tracker$iteration_added)
plot(NULL, xlim=c(0,1), ylim=c(0,1), main="alpha=.5"); text(m3e1_10$X, labels=m3e1_10$X_tracker$iteration_added)
plot(NULL, xlim=c(0,1), ylim=c(0,1), main="random"); text(m4e1_10$X, labels=m4e1_10$X_tracker$iteration_added)
```


## Comparison of intwerror

```{r compiledata, cache=F}
e1_aiw <- list(m1=m1e1_10$stats$actual_intwerror,
               m2=m2e1_10$stats$actual_intwerror,
               m3=m3e1_10$stats$actual_intwerror,
               m4=m4e1_10$stats$actual_intwerror)
e1_aiw2 <- reshape2::melt(e1_aiw)
print(str(e1_aiw2))
print(e1_aiw2$L)
e1_aiw2$iter <- rep(1:length(e1_aiw[[1]]), length(e1_aiw))
e1_aiw
```

## Comparison of intwerror

```{r plotintwerror, cache=F}
library(ggplot2)
ggplot(data=e1_aiw2, aes(x=iter, y=value, group=L1, color=L1)) + geom_line() + geom_point()  + scale_y_continuous(trans='log10') + 
  scale_color_hue(labels=expression(alpha==1,alpha==0,alpha==0.5,random))#c("$\alpha=1$",expression(z>0),.5,"random"))
```


## Comparison of mse

```{r compiledata_mse, cache=F}
e1_aiw_mse <- list(m1=m1e1_10$stats$mse,
                   m2=m2e1_10$stats$mse,
                   m3=m3e1_10$stats$mse,
                   m4=m4e1_10$stats$mse)
e1_aiw2_mse <- reshape2::melt(e1_aiw_mse)
print(str(e1_aiw2_mse))
print(e1_aiw2_mse$L)
e1_aiw2_mse$iter <- rep(1:length(e1_aiw_mse[[1]]), length(e1_aiw_mse))
e1_aiw_mse
```

## Comparison of mse

```{r plotintwerror_mse, cache=F}
library(ggplot2)
ggplot(data=e1_aiw2_mse, aes(x=iter, y=value, group=L1, color=L1)) + geom_line() + geom_point()  + scale_y_continuous(trans='log10') + 
  scale_color_hue(labels=expression(alpha==1,alpha==0,alpha==0.5,random))
```
