---
title: "Meeting 10/11/17"
author: "Collin Erickson"
date: "October 11, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE)
setwd("..//") # Will get reset, but need this to have source below work properly
source("adaptconcept2_sFFLHD_R6.R")
```

## Discussed last week

* Comparing how $1+\alpha$ affects results

* Try uncentered curve

* Clean code

## Progress

* $\mathbb{E}[1/||g(x)||^2]$ using gradient samples

## 1-D, $E[1/g(x)^2]$, no $1+\alpha$, behaves poorly

```{r, echo=F, message=F}
logistic <- function(x, offset, scl) {1 / (1 + exp(-scl*(x-offset)))}; 
logistic_plateau <- function(x) {logistic(x[1], .15, 15) - logistic(x[1], .85,15)}; #curve(Vectorize(logistic_plateau)(x)); #cf(logistic_plateau)
# grad_norm2_meaninv_plateau
invisible(capture.output({set.seed(2); csa(); a <- adapt.concept2.sFFLHD.R6$new(D=1,L=3,func=Vectorize(logistic_plateau), obj="desirability", des_func=des_func_grad_norm2inv_mean, alpha_des=1, weight_const = 0, n0=4, take_until_maxpvar_below=1, package="laGP_GauPro_kernel", design='sFFLHD', selection_method="max_des_red_all"); a$run(1)}))
```

## Batch 2
```{r, echo=F, message=F}
invisible(capture.output(a$run(1)))
```

## Batch 3
```{r, echo=F}
invisible(capture.output(a$run(1)))
```

## Batch 4
```{r, echo=F}
invisible(capture.output(a$run(1)))
```

## Batch 5
```{r, echo=F}
invisible(capture.output(a$run(1)))
```




## 2-D, $E[1/g(x)^2]$, no $1+\alpha$, behaves poorly

```{r, echo=F, message=F}
invisible(capture.output({set.seed(2); csa(); a <- adapt.concept2.sFFLHD.R6$new(D=2,L=3,func=function(x)logistic_plateau(x[1])*logistic_plateau(x[2]), obj="desirability", des_func=des_func_grad_norm2inv_mean, alpha_des=1, weight_const = 0, n0=8, take_until_maxpvar_below=1, package="laGP_GauPro_kernel", design='sFFLHD', selection_method="max_des_red_all", verbose=0); a$run(1)}))
```

## Batch 2
```{r, echo=F, message=F}
invisible(capture.output(a$run(1)))
```

## Batch 3
```{r, echo=F}
invisible(capture.output(a$run(1)))
```

## Batch 4
```{r, echo=F}
invisible(capture.output(a$run(1)))
```

## Batch 5
```{r, echo=F}
invisible(capture.output(a$run(1)))
```



## Compare how 1+$\alpha$ affects result

* $\delta = $

* $\omega = \delta$

* $\omega = 1 + \alpha \delta$

* $\omega = $ no E

## 1 + 100 $\delta$

```{r, echo=F, message=F}
invisible(capture.output({set.seed(2); csa(); a <- adapt.concept2.sFFLHD.R6$new(D=1,L=3,func=Vectorize(logistic_plateau), obj="desirability", des_func=des_func_grad_norm2_mean, alpha_des=1e2, n0=4, take_until_maxpvar_below=1, package="laGP_GauPro_kernel", design='sFFLHD', selection_method="max_des_red_all")}))
invisible(capture.output(a$run(4, plotlastonly = TRUE)))
```

## $\delta$

```{r, echo=F, message=F}
invisible(capture.output({set.seed(2); csa(); a <- adapt.concept2.sFFLHD.R6$new(D=1,L=3,func=Vectorize(logistic_plateau), obj="desirability", des_func=des_func_grad_norm2_mean, alpha_des=1, weight_const=0, n0=4, take_until_maxpvar_below=1, package="laGP_GauPro_kernel", design='sFFLHD', selection_method="max_des_red_all")}))
invisible(capture.output(a$run(4, plotlastonly = TRUE)))
```

## 3

```{r, echo=F, message=F}
invisible(capture.output({set.seed(2); csa(); a <- adapt.concept2.sFFLHD.R6$new(D=1,L=3,func=Vectorize(logistic_plateau), obj="desirability", des_func=des_func_mean_grad_norm2, alpha_des=1, weight_const=0, n0=4, take_until_maxpvar_below=1, package="laGP_GauPro_kernel", design='sFFLHD', selection_method="max_des_red_all")}))
invisible(capture.output(a$run(4, plotlastonly = TRUE)))
```


## 4

```{r, echo=F, message=F}
invisible(capture.output({set.seed(2); csa(); a <- adapt.concept2.sFFLHD.R6$new(D=1,L=3,func=Vectorize(logistic_plateau), obj="desirability", des_func=des_func_mean_grad_norm2, alpha_des=100, weight_const=1, n0=4, take_until_maxpvar_below=1, package="laGP_GauPro_kernel", design='sFFLHD', selection_method="max_des_red_all")}))
invisible(capture.output(a$run(4, plotlastonly = TRUE)))
```






## 1-D, $E[g(x)^2]$, no $1+\alpha$, single logistic

```{r, echo=F, message=F}
invisible(capture.output({set.seed(2); csa(); a <- adapt.concept2.sFFLHD.R6$new(D=1,L=3,func=Vectorize(function(xx)logistic(xx,.5,15)), obj="desirability", des_func=des_func_grad_norm2_mean, alpha_des=1, weight_const = 0, n0=4, take_until_maxpvar_below=1, package="laGP_GauPro_kernel", design='sFFLHD', selection_method="max_des_red_all"); a$run(1)}))
```

## Batch 2
```{r, echo=F, message=F}
invisible(capture.output(a$run(1)))
```

## Batch 3
```{r, echo=F}
invisible(capture.output(a$run(1)))
```

## Batch 4
```{r, echo=F}
invisible(capture.output(a$run(1)))
```

## Batch 5
```{r, echo=F}
invisible(capture.output(a$run(1)))
```




## 1-D, plateau 1/$E[g(x)^2]$, no $1+\alpha$, single logistic

```{r, echo=F, message=F}
invisible(capture.output({set.seed(2); csa(); a <- adapt.concept2.sFFLHD.R6$new(D=1,L=3,func=Vectorize(function(xx)logistic(xx,.5,15)), obj="desirability", des_func=des_func_grad_norm2_meaninv_plateau, alpha_des=1, weight_const = 0, n0=4, take_until_maxpvar_below=1, package="laGP_GauPro_kernel", design='sFFLHD', selection_method="max_des_red_all"); a$run(1)}))
```

## Batch 2
```{r, echo=F, message=F}
invisible(capture.output(a$run(1)))
```

## Batch 3
```{r, echo=F}
invisible(capture.output(a$run(1)))
```

## Batch 4
```{r, echo=F}
invisible(capture.output(a$run(1)))
```

## Batch 5
```{r, echo=F}
invisible(capture.output(a$run(1)))
```
